Cross Validation Approaches for Penalized Cox Regression

### 2018-05-26 main.tex
Removed note
Edit to final paragraph of introduction

%We hope to improve cross-validation procedure for Cox regression to achieve a good balance between stability and performance.

In this paper, we propose two alternative ways to carry out cross validation. Instead of cross-validating over partial likelihood, we propose to cross validate over the linear predictors of the regression model and cross validate over the deviance residual \citep{Therneau1990}of the Cox model. We conducted simulation studies to compare how those methods perform in both low dimensional and high dimensional settings with LASSO penalty. We compared the two proposed methods with the existing cross-validated partial likelihood approaches. We showed that the linear predictor approach outperforms other cross validation approaches in various scenarios. We found out that using cross validation to select tuning parameters for LASSO penalized cox regression tends to be a conservative approach in general. Finally, we apply those methods to two high dimensional data sets from real studies with time-to-event outcomes.

@@

\note{Move this paragraph to Section 2?} In the Cox model, the hazard function for subject $i$ is given by 
\begin{equation}
  h_{i}(t) = h_{0}(t) \text{exp}( X_{i}^{T} \beta),
\end{equation} 
where $h_{0}$ is the baseline hazard and $e^{X_i^{T} \beta}$ is the risk for subject $i$ with covariates $X_i$ relative to that baseline.  The estimation of the coefficients is obtained by maximizing a partial likelihood.  Letting $t_i$ denote the time on study for subject $i$ and $\delta_{i}$ indicate whether or not an event is observed for subject $i$, each subject's individual contribution to that partial likelihood is
\begin{equation}
  l_{i}(\beta) = \left \{\frac{\text{exp} ( X_{i}^{T} \beta)}{\sum_{ k \in R(t_{i})}\text{exp} ( X_{k}^{T} \beta)}\right \}^{\delta_{i}},
\end{equation}
where $R(t_{i})$ denotes the set of observations at risk at time $t_{i}$.  The partial likelihood for the entire sample of $n$ subjects is then given by:
\begin{equation}
  L(\beta) =\prod_{i = 1}^{n} l_{i}(\beta).
\end{equation}
%% \begin{equation}
%%   L(\beta) =\prod_{i = 1}^{n} l_{i}(\beta) = \prod_{j=1}^{m} \frac{\text{exp} ( X_{j}^{T} \beta)}{\sum_{ k \in R(t_{j})}\text{exp} ( X_{k}^{T} \beta)}.
%% \end{equation}

>>>>

In this paper, we propose two alternative ways to carry out cross validation for Cox regression. Instead of cross-validating over partial likelihood, we propose cross validation over either the linear predictors of the regression model or over the deviance residuals \citep{Therneau1990}. Through simulation studies, we compare these proposed methods with existing cross-validation approaches for LASSO penalized Cox regression in both low- and high-dimensional settings.  We find that all cross validation approaches tend to be conservative, but that the linear predictor approach offers the best combination of performance and stability, and we recommend using it for regularization parameter selection in penalized Cox models.  We conclude by applying both proposed and existing approaches to two high dimensional data sets from real studies with time-to-event outcomes.

@@

In the Cox model, the hazard function for subject $i$ is given by 
\begin{equation}
  h_{i}(t) = h_{0}(t) \text{exp}( X_{i}^{T} \beta),
\end{equation} 
where $h_{0}$ is the baseline hazard and $e^{X_i^{T} \beta}$ is the risk for subject $i$ with covariates $X_i$ relative to that baseline.  The estimation of the coefficients is obtained by maximizing a partial likelihood.  Letting $t_i$ denote the time on study for subject $i$ and $\delta_{i}$ indicate whether or not an event is observed for subject $i$, each subject's individual contribution to that partial likelihood is
\begin{equation}
  l_{i}(\beta) = \left \{\frac{\text{exp} ( X_{i}^{T} \beta)}{\sum_{ k \in R(t_{i})}\text{exp} ( X_{k}^{T} \beta)}\right \}^{\delta_{i}},
\end{equation}
where $R(t_{i})$ denotes the set of observations at risk at time $t_{i}$.  The partial likelihood for the entire sample of $n$ subjects is then given by:
\begin{equation}
  L(\beta) =\prod_{i = 1}^{n} l_{i}(\beta).
\end{equation}
%% \begin{equation}
%%   L(\beta) =\prod_{i = 1}^{n} l_{i}(\beta) = \prod_{j=1}^{m} \frac{\text{exp} ( X_{j}^{T} \beta)}{\sum_{ k \in R(t_{j})}\text{exp} ( X_{k}^{T} \beta)}.
%% \end{equation}
